This is an example of article title

### 2019-08-28 paper/paper.tex
Added Survival.jl manual reference.
Updates from Overleaf

The regression analysis ecosystem in Julia has GLM.jl \cite{GLM.jl} as its flagship. GLM.jl provides the typical functionality for fitting generalized linear models through Fisher scoring. This includes linear models, Poisson/Negative Binomial, Logit/Probit, and other non-canonical link models. CovarianceMatrices.jl \cite{CovarianceMatrices.jl} provides various variance covariance estimators for GLM.jl models à la R's
sandwich package. LinearMixedModels.jl \cite{LinearMixedModels} extends GLM.jl for mixed-effects models. FixedEffectModels.jl provides fast estimation of linear models with instrumental variables and high dimensional categorical variables à la reghdfe. Survival.jl provides a series of estimators for duration models. Two major gaps in the ecosystem include estimating nominal and ordinal response models (i.e., discrete choice) with more than two alternatives and support for longitudinal estimators.

@@

The syntax to estimate a model follows the StatsBase API which provides two methods for building and estimating models (i.e., \textit{fit} and \textit{fit!}). The \textit{fit} approach takes (1) an estimator, (2) a model formula, (3) data, and additional arguments depending on the model. \textit{EconometricModel} is the generic estimator which dispatches to continuous, nominal or ordinal response models automatically based on the type of the response. Other estimators are available and the following figures illustrate some of the use cases.

@@

\newpage

>>>>

The regression analysis ecosystem in Julia has GLM.jl \cite{GLM.jl} as its flagship. GLM.jl provides the typical functionality for fitting generalized linear models through Fisher scoring. This includes linear models, Poisson/Negative Binomial, Logit/Probit, and other non-canonical link models. CovarianceMatrices.jl \cite{CovarianceMatrices.jl} provides various variance covariance estimators for GLM.jl models à la R's
sandwich package. MixedModels.jl \cite{MixedModels.jl} extends GLM.jl for mixed-effects models. FixedEffectModels.jl provides fast estimation of linear models with instrumental variables and high dimensional categorical variables à la reghdfe. Survival.jl \cite{Survival.jl} provides a series of estimators for duration models. Two major gaps in the ecosystem include estimating nominal and ordinal response models (i.e., discrete choice) with more than two alternatives and support for longitudinal estimators.

@@

The syntax to estimate a model follows the StatsBase API which provides a method for building and estimating models (i.e., \textit{fit}). The \textit{fit} approach takes (1) an estimator, (2) a model formula, (3) data, and additional arguments depending on the model. \textit{EconometricModel} is the generic estimator which dispatches to continuous, nominal or ordinal response models automatically based on the type of the response. Other estimators are available and the following figures illustrate some of the use cases.

@@
